Title
========================================================

brand similar

```{r}
head(user_brand)
dim(user_brand)
```



以30天是否购买因变量，
其余变量为自变量
逻辑回归

user_brand$is_buy[user_brand$last_30_day_buy_times > 0]  <-1
user_brand$is_buy[user_brand$last_30_day_buy_times == 0]  <- 0
user_brand$is_buy <- factor(user_brand$is_buy,
                            levels = c(0,1),
                            labels = c("No","Yes"))

user_brand2 <- user_brand[-c(1,2,17)]
head(user_brand2)

logistic.fit <- glm(is_buy ~ .,
  family = binomial(),
	data = user_brand2);

summary(logistic.fit)

class(user_brand$is_buy)
  

sub_last_30_days_buy <- subset(user_brand,last_30_day_buy_times != 0)

dim(sub_last_30_days_buy)
head(sub_last_30_days_buy)


3个月内
1.点击数 click_num
```{r}
table(user_brand$click_num)
summary(user_brand$click_num)
summary(user_brand$click_buy_ratio)

```
  0次 0分
  1次 1分
  2次 2次
  3次 3分
  3次以上 4分

2.是否收藏 collect_num
```{r}
table(user_brand$collect_num)
summary(user_brand$collect_num)
summary(user_brand$collect_buy_ratio)
```
  0次 0分
  1次 1分
  2次 2次
  2次以上 4分

3.是否购物车 cart_num
```{r}
table(user_brand$cart_num)
summary(user_brand$cart_num)
summary(user_brand$cart_buy_ratio)
```
  0次 0分
  1次 2分
  1次以上 4分
  
4.是否购买 buy_num
```{r}
table(user_brand$buy_num)
summary(user_brand$buy_num)
```
  0次 0分
  1次 1分
  2次 2次
  2次以上 4分


计算评分
```{r}
head(user_brand)

#通过函数调用失败，后期再调试
#user_brand$score <- compute_click_score(user_brand$click_num)
#user_brand$score <- apply(user_brand,1,computeScore)

user_brand$score <- 0


#click
user_brand$temp <- 0
user_brand$temp[user_brand$click_num == 1] <- 1
user_brand$temp[user_brand$click_num == 2] <- 2
user_brand$temp[user_brand$click_num == 3] <- 3
user_brand$temp[user_brand$click_num > 3] <- 4
user_brand$score<- user_brand$score+user_brand$temp

#collect
user_brand$temp <- 0
user_brand$temp[user_brand$collect_num == 1] <- 1
user_brand$temp[user_brand$collect_num == 2] <- 2
user_brand$temp[user_brand$collect_num > 2] <- 4
user_brand$score<- user_brand$score+user_brand$temp

#cart
user_brand$temp <- 0
user_brand$temp[user_brand$cart_num == 1] <- 2
user_brand$temp[user_brand$cart_num == 2] <- 4
user_brand$score<- user_brand$score+user_brand$temp

#buy
user_brand$temp <- 0
user_brand$temp[user_brand$buy_num == 1] <- 1
user_brand$temp[user_brand$buy_num == 2] <- 2
user_brand$temp[user_brand$buy_num > 2] <- 4
user_brand$score<- user_brand$score+user_brand$temp

table(user_brand$score)


head(user_brand)
dim(user_brand)
user_brand_score <- user_brand[c(1,2,12)]
head(user_brand_score)



save(user_brand_score,file ='data/user_brand_score.RData')
write.csv(user_brand_score,file="data/user_brand_score.csv")

```






```{r}
computeScore <-function(data){
  click_score <- compute_click_score(data$click_num) + 
    compute_collect_score(data$collect_num) +
    compute_cart_score(data$cart_num) +
    compute_buy_score(data$buy_num)
  
}


compute_click_score <- function(num) {
    if(num == 1) {
       2
    }else if (num == 2) {
       2
    }else if (num == 3) {
       3
    }else if (num > 3) {
       4
    }else {
       0
    }
}


compute_collect_score <- function(num) {
    if(num == 1) {
       1
    }else if (num == 2) {
       2
    }else if (num > 2) {
       4
    }else {
       0
    }
}

compute_cart_score <- function(num) {
    if(num == 1) {
       1
    }else if (num > 1) {
       4
    }else {
       0
    }
}

compute_buy_score <- function(num) {
    if(num == 1) {
       1
    }else if (num == 2) {
       2
    }else if (num > 2) {
       4
    }else {
       0
    }
}






x <- 1
if (x ==1){
     print('same')
 } else if (x > 1){
     print('bigger')
 } else {
     print('smaller')
 }


```
  



